Check experimental design

### 2023-05-08 analysis/01_experimental-design.Rmd
Set-up for aggregate-coded interaction terms

>>>>

# Aggregate-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions. Here we do it by aggregating up the interaction terms.

```{r aggregate-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

# Build out all the necessary interactions...
# ...by multiplying together the needed index-coded levels.
    smalldonors_criticized = fund1 * gov_rel2,
    smalldonors_crackdown = fund1 * gov_rel3,
    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
    nottransp_criticized = transp1 * gov_rel2,
    nottransp_crackdown = transp1 * gov_rel3,
    nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
    nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
    nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
    nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
    nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "aggregate_interactions.csv"))
```
